---
title: "Correlation_BERT_Ranking"
author: "Emily Kratsch"
format: html
editor: visual
---

# All 8 Items

## DQE:

### Kendall Correlation

```{r}
# Step 1: Create the data
items <- c("T1", "T2", "T3", "T4", "T5", "T6", "T7", "T8")
dqe <- c(3.98, 3.9, 4.18, 1.6, 4.02, 1.42, 4.22, 1.4)
cosine_score <- c(0.9417274594306946, 0.8403416872024536, 0.9163545370101929, 0.6848716139793396, 0.9321397542953491, 0.5273422002792358, 0.9175342321395874, 0.24246227741241455)


```

```{r}
# Step 2: Create a data frame
data <- data.frame(items, dqe, cosine_score)


```

```{r}
# Step 3 Normality 
shapiro.test(data$dqe)
shapiro.test(data$cosine_score)


```

```{r}
# Step 1: Perform Kendall's Tau hypothesis test
kendall_test <- cor.test(data$dqe, data$cosine_score, method = "kendall", alternative = "greater")
print(kendall_test)
```

### Visualisation

```{r}
# Step 2: Rank the data
ranked_dqe <- rank(data$dqe)
ranked_cosine_score <- rank(data$cosine_score)

# Step 3: Visualize the ranked data with a scatter plot
plot(ranked_dqe, ranked_cosine_score, 
     main = "Scatterplot of Ranked DQE vs. Ranked Cosine Score",
     xlab = "Ranked DQE", 
     ylab = "Ranked Cosine Score",
     pch = 19, col = "blue")

# Add a LOESS smooth line to show the trend in ranks
lines(loess.smooth(ranked_dqe, ranked_cosine_score), col = "red", lwd = 2)

# Optional: Jitter the points to better visualize any overlapping ranks
plot(jitter(ranked_dqe), jitter(ranked_cosine_score), 
     main = "Jittered Scatterplot of Ranked DQE vs. Ranked Cosine Score",
     xlab = "Ranked DQE (Jittered)", 
     ylab = "Ranked Cosine Score (Jittered)",
     pch = 19, col = "blue")

# Add LOESS smooth line to jittered plot
lines(loess.smooth(jitter(ranked_dqe), jitter(ranked_cosine_score)), col = "red", lwd = 2)
```

## DQE Honesty:

### Kendall Correlation

```{r}
# Step 1: Create the data
items <- c("T1", "T2", "T3", "T4", "T5", "T6", "T7", "T8")
dqeH <- c(3.72, 3.52, 4.12, 1.52, 4.00, 1.20, 3.76, 1.12)
cosine_score <- c(0.9417274594306946, 0.8403416872024536, 0.9163545370101929, 0.6848716139793396, 0.9321397542953491, 0.5273422002792358, 0.9175342321395874, 0.24246227741241455)


```

```{r}
# Step 2: Create a data frame
data <- data.frame(items, dqeH, cosine_score)


```

```{r}
# Step 3 Normality 
shapiro.test(data$dqeH)
shapiro.test(data$cosine_score)


```

```{r}
# Step 1: Perform Kendall's Tau hypothesis test
kendall_test <- cor.test(data$dqeH, data$cosine_score, method = "kendall", alternative = "greater")
print(kendall_test)
```

## DQE Comprehensibility:

### Kendall Correlation

```{r}
# Step 1: Create the data
items <- c("T1", "T2", "T3", "T4", "T5", "T6", "T7", "T8")
dqeC <- c(4.24, 4.28, 4.24, 1.68, 4.04, 1.64, 4.78, 1.68)
cosine_score <- c(0.9417274594306946, 0.8403416872024536, 0.9163545370101929, 0.6848716139793396, 0.9321397542953491, 0.5273422002792358, 0.9175342321395874, 0.24246227741241455)


```

```{r}
# Step 2: Create a data frame
data <- data.frame(items, dqeC, cosine_score)


```

```{r}
# Step 3 Normality 
shapiro.test(data$dqeC)
shapiro.test(data$cosine_score)


```

```{r}
# Step 1: Perform Kendall's Tau hypothesis test
kendall_test <- cor.test(data$dqeC, data$cosine_score, method = "kendall", alternative = "greater")
print(kendall_test)
```

## Binary Decision Analysis

### Kendall Coorelation

```{r}
# Data preparation
items <- c("T1", "T2", "T3", "T4", "T5", "T6", "T7", "T8")
bdscore <- c(42, 35, 47, 6, 38, 8, 45, 6)
cosine_score <- c(0.9417274594306946, 0.8403416872024536, 0.9163545370101929, 0.6848716139793396, 0.9321397542953491, 0.5273422002792358, 0.9175342321395874, 0.24246227741241455)

data <- data.frame(items, bdscore, cosine_score)

# Normality tests
shapiro_test_bdscore <- shapiro.test(data$bdscore)
shapiro_test_cosine <- shapiro.test(data$cosine_score)

# Print results
shapiro_test_bdscore
shapiro_test_cosine

```

```{r}
# Step 2: Perform Kendall's Tau correlation test
kendall_test <- cor.test(data$bdscore, data$cosine_score, method = "kendall", alternative = "greater")

# Print the Kendall's Tau test result
print(kendall_test)

```

### Visualisation

```{r}
# Step 3: Rank the data
ranked_bdscore <- rank(data$bdscore)
ranked_cosine_score <- rank(data$cosine_score)

# Step 4: Visualize the ranked data with a scatter plot
plot(ranked_bdscore, ranked_cosine_score, 
     main = "Scatterplot of Ranked BDScore vs. Ranked Cosine Score",
     xlab = "Ranked BDScore", 
     ylab = "Ranked Cosine Score",
     pch = 19, col = "blue")

# Add a LOESS smooth line to show the trend in ranks
lines(loess.smooth(ranked_bdscore, ranked_cosine_score), col = "red", lwd = 2)

# Optional: Jitter the points to better visualize any overlapping ranks
plot(jitter(ranked_bdscore), jitter(ranked_cosine_score), 
     main = "Jittered Scatterplot of Ranked BDScore vs. Ranked Cosine Score",
     xlab = "Ranked BDScore (Jittered)", 
     ylab = "Ranked Cosine Score (Jittered)",
     pch = 19, col = "blue")

# Add LOESS smooth line to jittered plot
lines(loess.smooth(jitter(ranked_bdscore), jitter(ranked_cosine_score)), col = "red", lwd = 2)
```

## Binary Dec Honesty:

### Kendall Correlation

```{r}
# Step 1: Create the data
items <- c("T1", "T2", "T3", "T4", "T5", "T6", "T7", "T8")
bdscoreH <- c(19, 13, 24, 2, 16, 2, 20, 0)
cosine_score <- c(0.9417274594306946, 0.8403416872024536, 0.9163545370101929, 0.6848716139793396, 0.9321397542953491, 0.5273422002792358, 0.9175342321395874, 0.24246227741241455)


```

```{r}
# Step 2: Create a data frame
data <- data.frame(items, bdscoreH, cosine_score)


```

```{r}
# Step 3 Normality 
shapiro.test(data$bdscoreH)
shapiro.test(data$cosine_score)


```

```{r}
# Step 1: Perform Kendall's Tau hypothesis test
kendall_test <- cor.test(data$bdscoreH, data$cosine_score, method = "kendall", alternative = "greater")
print(kendall_test)
```

## Binary Dec Comprehensibility:

### Kendall Correlation

```{r}
# Step 1: Create the data
items <- c("T1", "T2", "T3", "T4", "T5", "T6", "T7", "T8")
bdscoreC <- c(23, 22, 23, 4, 22, 6, 25, 6)
cosine_score <- c(0.9417274594306946, 0.8403416872024536, 0.9163545370101929, 0.6848716139793396, 0.9321397542953491, 0.5273422002792358, 0.9175342321395874, 0.24246227741241455)


```

```{r}
# Step 2: Create a data frame
data <- data.frame(items, bdscoreC, cosine_score)


```

```{r}
# Step 3 Normality 
shapiro.test(data$bdscoreC)
shapiro.test(data$cosine_score)


```

```{r}
# Step 1: Perform Kendall's Tau hypothesis test
kendall_test <- cor.test(data$bdscoreC, data$cosine_score, method = "kendall", alternative = "greater")
print(kendall_test)
```

## A/B test:

### Kendall Coorelation

```{r}
# Step 1: Prepare the new data
items <- c("T1", "T2", "T3", "T4", "T5", "T6", "T7", "T8")
abscore <- c(177, 156, 206, 20, 204, 11, 233, 16)
cosine_score <- c(0.9417274594306946, 0.8403416872024536, 0.9163545370101929, 
                  0.6848716139793396, 0.9321397542953491, 0.5273422002792358, 
                  0.9175342321395874, 0.24246227741241455)

# Combine into a data frame
data <- data.frame(items, abscore, cosine_score)
```

```{r}
# Step 2: Check for normality using Shapiro-Wilk test
shapiro_test_abscore <- shapiro.test(data$abscore)
shapiro_test_cosine <- shapiro.test(data$cosine_score)

# Print results of normality tests
print(shapiro_test_abscore)
print(shapiro_test_cosine)
```

```{r}
# Step 3: Perform Kendall's Tau correlation test (due to potential non-normality and ties)
kendall_test <- cor.test(data$abscore, data$cosine_score, method = "kendall", alternative = "greater")
print(kendall_test)

```

### Visualisation

```{r}
# Step 1: Rank the data
ranked_abscore <- rank(data$abscore)
ranked_cosine_score <- rank(data$cosine_score)

# Step 2: Visualize the ranked data with a scatter plot
plot(ranked_abscore, ranked_cosine_score, 
     main = "Scatterplot of Ranked ABScore vs. Ranked Cosine Score",
     xlab = "Ranked ABScore", 
     ylab = "Ranked Cosine Score",
     pch = 19, col = "blue")

# Step 3: Add a LOESS smooth line to show the trend in ranks
lines(loess.smooth(ranked_abscore, ranked_cosine_score), col = "red", lwd = 2)

# Optional: Jitter the points to better visualize any overlapping ranks
plot(jitter(ranked_abscore), jitter(ranked_cosine_score), 
     main = "Jittered Scatterplot of Ranked ABScore vs. Ranked Cosine Score",
     xlab = "Ranked ABScore (Jittered)", 
     ylab = "Ranked Cosine Score (Jittered)",
     pch = 19, col = "blue")

# Step 4: Add LOESS smooth line to jittered plot
lines(loess.smooth(jitter(ranked_abscore), jitter(ranked_cosine_score)), col = "red", lwd = 2)

```

### Visualisation raw Data

```{r}
# Step 4: Visualize the results with a scatter plot and trend lines
plot(data$abscore, data$cosine_score, 
     main = "Scatterplot of ABScore vs. Cosine Score", 
     xlab = "ABScore", 
     ylab = "Cosine Score", 
     pch = 19, col = "blue")

# Add a LOESS smooth line to show the trend
lines(loess.smooth(data$abscore, data$cosine_score), col = "red", lwd = 2)

# Optional: Add a linear regression line to show the general trend
#abline(lm(cosine_score ~ abscore, data = data), col = "green")
```

## AB Honesty:

### Kendall Correlation

```{r}
# Step 1: Create the data
items <- c("T1", "T2", "T3", "T4", "T5", "T6", "T7", "T8")
abscoreH <- c(101, 79, 117, 18, 117, 0, 133, 0)
cosine_score <- c(0.9417274594306946, 0.8403416872024536, 0.9163545370101929, 0.6848716139793396, 0.9321397542953491, 0.5273422002792358, 0.9175342321395874, 0.24246227741241455)

```

```{r}
# Step 2: Create a data frame
data <- data.frame(items, abscoreH, cosine_score)


```

```{r}
# Step 3 Normality 
shapiro.test(data$abscoreH)
shapiro.test(data$cosine_score)


```

```{r}
# Step 1: Perform Kendall's Tau hypothesis test
kendall_test <- cor.test(data$abscoreH, data$cosine_score, method = "kendall", alternative = "greater")
print(kendall_test)
```

## AB Comprehensibility:

### Kendall Correlation

```{r}
# Step 1: Create the data
items <- c("T1", "T2", "T3", "T4", "T5", "T6", "T7", "T8")
abscoreC <- c(76, 77, 89, 2, 87, 11, 100, 16)
cosine_score <- c(0.9417274594306946, 0.8403416872024536, 0.9163545370101929, 0.6848716139793396, 0.9321397542953491, 0.5273422002792358, 0.9175342321395874, 0.24246227741241455)

```

```{r}
# Step 2: Create a data frame
data <- data.frame(items, abscoreC, cosine_score)


```

```{r}
# Step 3 Normality 
shapiro.test(data$abscoreC)
shapiro.test(data$cosine_score)


```

```{r}
# Step 1: Perform Kendall's Tau hypothesis test
kendall_test <- cor.test(data$abscoreC, data$cosine_score, method = "kendall", alternative = "greater")
print(kendall_test)
```

## BWS: Kendalls Tau

### Kendall Coorelation

```{r}
# Step 1: Prepare the new data
items <- c("T1", "T2", "T3", "T4", "T5", "T6", "T7", "T8")
bwsscore <- c(25, 19, 29, -44, 30, -36, 31, -54)
cosine_score <- c(0.9417274594306946, 0.8403416872024536, 0.9163545370101929, 
                  0.6848716139793396, 0.9321397542953491, 0.5273422002792358, 
                  0.9175342321395874, 0.24246227741241455)

# Combine into a data frame
data <- data.frame(items, bwsscore, cosine_score)
```

```{r}
# Step 2: Check for normality using Shapiro-Wilk test
shapiro_test_bwsscore <- shapiro.test(data$bwsscore)
shapiro_test_cosine <- shapiro.test(data$cosine_score)

# Print results of normality tests
print(shapiro_test_bwsscore)
print(shapiro_test_cosine)
```

```{r}
# Step 3: Perform Kendall's Tau correlation test
kendall_test <- cor.test(data$bwsscore, data$cosine_score, method = "kendall", alternative = "greater")
print(kendall_test)
```

### Visualisation

```{r}
# Step 1: Rank the data
ranked_bwsscore <- rank(data$bwsscore)
ranked_cosine_score <- rank(data$cosine_score)

# Step 2: Visualize the ranked data with a scatter plot
plot(ranked_bwsscore, ranked_cosine_score, 
     main = "Scatterplot of Ranked BWSScore vs. Ranked Cosine Score",
     xlab = "Ranked BWSScore", 
     ylab = "Ranked Cosine Score",
     pch = 19, col = "blue")

# Step 3: Add a LOESS smooth line to show the trend in ranks
lines(loess.smooth(ranked_bwsscore, ranked_cosine_score), col = "red", lwd = 2)

# Optional: Jitter the points to better visualize any overlapping ranks
plot(jitter(ranked_bwsscore), jitter(ranked_cosine_score), 
     main = "Jittered Scatterplot of Ranked BWSScore vs. Ranked Cosine Score",
     xlab = "Ranked BWSScore (Jittered)", 
     ylab = "Ranked Cosine Score (Jittered)",
     pch = 19, col = "blue")

# Step 4: Add LOESS smooth line to jittered plot
lines(loess.smooth(jitter(ranked_bwsscore), jitter(ranked_cosine_score)), col = "red", lwd = 2)

```

### Visualisation raw data

```{r}
# Step 4: Visualize the results with a scatter plot and trend lines
plot(data$bwsscore, data$cosine_score, 
     main = "Scatterplot of BWSScore vs. Cosine Score", 
     xlab = "BWSScore", 
     ylab = "Cosine Score", 
     pch = 19, col = "blue")

# Add a LOESS smooth line to show the trend
lines(loess.smooth(data$bwsscore, data$cosine_score), col = "red", lwd = 2)

# Optional: Add a linear regression line to show the general trend
#abline(lm(cosine_score ~ bwsscore, data = data), col = "green")
```

## BWS Honesty:

### Kendall Correlation

```{r}
# Step 1: Create the data
items <- c("T1", "T2", "T3", "T4", "T5", "T6", "T7", "T8")
bwsscoreH <- c(7, 5, 15, -25, 16, -12, 21, -27)
cosine_score <- c(0.9417274594306946, 0.8403416872024536, 0.9163545370101929, 0.6848716139793396, 0.9321397542953491, 0.5273422002792358, 0.9175342321395874, 0.24246227741241455)


```

```{r}
# Step 2: Create a data frame
data <- data.frame(items, bwsscoreH, cosine_score)


```

```{r}
# Step 3 Normality 
shapiro.test(data$bwsscoreH)
shapiro.test(data$cosine_score)


```

```{r}
# Step 1: Perform Kendall's Tau hypothesis test
kendall_test <- cor.test(data$bwsscoreH, data$cosine_score, method = "kendall", alternative = "greater")
print(kendall_test)
```

## BWS Comprehensibility:

### Kendall Correlation

```{r}
# Step 1: Create the data
items <- c("T1", "T2", "T3", "T4", "T5", "T6", "T7", "T8")
bwsscoreC <- c(18, 14, 14, -19, 14, -24, 10, -27)
cosine_score <- c(0.9417274594306946, 0.8403416872024536, 0.9163545370101929, 0.6848716139793396, 0.9321397542953491, 0.5273422002792358, 0.9175342321395874, 0.24246227741241455)

```

```{r}
# Step 2: Create a data frame
data <- data.frame(items, bwsscoreC, cosine_score)


```

```{r}
# Step 3 Normality 
shapiro.test(data$bwsscoreC)
shapiro.test(data$cosine_score)


```

```{r}
# Step 1: Perform Kendall's Tau hypothesis test
kendall_test <- cor.test(data$bwsscoreC, data$cosine_score, method = "kendall", alternative = "greater")
print(kendall_test)
```

# 4 LLMs

## DQE

### Kendall Coorelation

```{r}
# Data preparation
items <- c("T1", "T2", "T3", "T4")
dqe <- c(3.94, 2.89, 2.72, 3.81)
cosine_score <- c(1.782069147, 1.601226151, 1.459481955, 1.15999651)

data <- data.frame(items, dqe, cosine_score)
```

```{r}
# Normality tests
shapiro_test_dqe <- shapiro.test(data$dqe)
shapiro_test_cosine <- shapiro.test(data$cosine_score)

# Print results
shapiro_test_dqe
shapiro_test_cosine

```

```{r}
# Step 2: Perform Kendall's Tau correlation test
kendall_test <- cor.test(data$dqe, data$cosine_score, method = "kendall", alternative = "greater")

# Print the Kendall's Tau test result
print(kendall_test)
## Binary Decision Analysis
### Kendall Coorelation

```

## Binary Decision Analysis

### Kendall Coorelation

```{r}
# Data preparation
items <- c("T1", "T2", "T3", "T4")
bdscore <- c(77, 53, 46, 51)
cosine_score <- c(1.782069147, 1.601226151, 1.459481955, 1.15999651)

data <- data.frame(items, bdscore, cosine_score)
```

```{r}
# Normality tests
shapiro_test_bdscore <- shapiro.test(data$bdscore)
shapiro_test_cosine <- shapiro.test(data$cosine_score)

# Print results
shapiro_test_bdscore
shapiro_test_cosine

```

```{r}
# Step 2: Perform Kendall's Tau correlation test
kendall_test <- cor.test(data$bdscore, data$cosine_score, method = "kendall", alternative = "greater")

# Print the Kendall's Tau test result
print(kendall_test)
## Binary Decision Analysis
### Kendall Coorelation

```

## A/B test:

### Kendall Coorelation

```{r}
# Data preparation
items <- c("T1", "T2", "T3", "T4")
abscore <- c(333, 226, 215, 249)
cosine_score <- c(1.782069147, 1.601226151, 1.459481955, 1.15999651)

data <- data.frame(items, abscore, cosine_score)
```

```{r}
# Normality tests
shapiro_test_abscore <- shapiro.test(data$abscore)
shapiro_test_cosine <- shapiro.test(data$cosine_score)

# Print results
shapiro_test_abscore
shapiro_test_cosine

```

```{r}
# Step 2: Perform Kendall's Tau correlation test
kendall_test <- cor.test(data$abscore, data$cosine_score, method = "kendall", alternative = "greater")

# Print the Kendall's Tau test result
print(kendall_test)
## Binary Decision Analysis
### Kendall Coorelation

```

## BWS

### Kendall Coorelation

```{r}
# Data preparation
items <- c("T1", "T2", "T3", "T4")
bwsscore <- c(44, -15, -6, -13)
cosine_score <- c(1.782069147, 1.601226151, 1.459481955, 1.15999651)

data <- data.frame(items, bwsscore, cosine_score)
```

```{r}
# Normality tests
shapiro_test_bwsscore <- shapiro.test(data$bwsscore)
shapiro_test_cosine <- shapiro.test(data$cosine_score)

# Print results
shapiro_test_bwsscore
shapiro_test_cosine

```

```{r}
# Step 2: Perform Kendall's Tau correlation test
kendall_test <- cor.test(data$bwsscore, data$cosine_score, method = "kendall", alternative = "greater")

# Print the Kendall's Tau test result
print(kendall_test)
## Binary Decision Analysis
### Kendall Coorelation

```

Tabllen

```{r}
library(flextable)
library(officer)
library(dplyr)

# Step 2: Create the data frame
data <- data.frame(
  Items = c("T1", "T2", "T3", "T4", "T5", "T6", "T7", "T8"),
  DQE = c(3.98, 3.90, 4.18, 1.60, 4.02, 1.42, 4.22, 1.40),
  BDScore = c(42, 35, 47, 6, 38, 8, 45, 6),
  ABScore = c(177, 156, 206, 20, 204, 11, 233, 16),
  BWSScore = c(25, 19, 29, -44, 30, -36, 31, -54),
  Cosine_Score = c(0.9417, 0.8403, 0.9164, 0.6849, 0.9321, 0.5273, 0.9175, 0.2425)
)

# Step 3: Create a flextable (APA style)
apa_table <- flextable(data) %>%
  theme_box() %>%
  set_table_properties(width = 0.5, layout = "autofit") %>%
  set_header_labels(
    Items = "Items", 
    DQE = "DQE", 
    BDScore = "BDScore", 
    ABScore = "ABScore", 
    BWSScore = "BWSScore", 
    Cosine_Score = "Cosine Score"
  ) %>%
  colformat_num(j = c("DQE", "Cosine_Score"), digits = 2) %>%  # Format numbers to 2 decimal places
  align(j = c("DQE", "BDScore", "ABScore", "BWSScore", "Cosine_Score"), align = "center") %>%
  autofit()

# Step 4: Save as Word document
doc <- read_docx() %>%
  body_add_flextable(value = apa_table)

# Save to file
print(doc, target = "APA_Style_Table.docx")
```

```{r}

# Load necessary libraries
##library(gt)

# Step 1: Prepare the data frame
#data <- tibble(
#  Items = c("T1", "T2", "T3", "T4", "T5", "T6", "T7", "T8"),
#  DQE = c(3.98, 3.90, 4.18, 1.60, 4.02, 1.42, 4.22, 1.40),
#  BDScore = c(42, 35, 47, 6, 38, 8, 45, 6),
#  ABScore = c(177, 156, 206, 20, 204, 11, 233, 16),
#  BWSScore = c(25, 19, 29, -44, 30, -36, 31, -54),
#  Cosine_Score = c(0.9417, 0.8403, 0.9164, 0.6849, 0.9321, 0.5273, 0.9175, 0.2425)
#)

# Step 2: Create the APA-style table using gt
#apa_table <- data %>%
#  gt() %>%
#  gt::cols_label(
#    Items = "Items",
#    DQE = "DQE",
#    BDScore = "BDScore",
#    ABScore = "ABScore",
#    BWSScore = "BWSScore",
#    Cosine_Score = "Cosine Score"
#  ) %>%
#  gt::fmt_number(columns = vars(DQE, Cosine_Score), decimals = 4) %>%
#  gt::tab_header(
#    title = "Mean Test Scores and Cosine Score per Generated Text"
#  ) %>%
#  gt::tab_style(
#    style = cell_text(weight = "bold"),
#    locations = cells_column_labels(everything())
#  ) %>%
#  gt::tab_options(
#    table.font.size = 12,
#    heading.align = "center"
#  )

# Print the table
#apa_table

# Optionally save the table as an image or HTML
#gtsave(apa_table, "MeansTable.docx")


```
